Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-02-14 paper/paper.tex
feat: overview of precice distribution

To see how well Nix can be used to build and package scientific software reliably and reproducibly, we conduct a case study in the context of the latest preCICE distribution, which is currently preCICE \texttt{v2211.0}.
The preCICE distribution consists out of the preCICE core library, as well as some tools, bindings, adapters, tutorials, the website and documentation, and the preCICE VM\footnote{\url{https://precice.org/installation-distribution.html}}.

>>>>

To see how well Nix can be used to build and package scientific software reliably and reproducibly, we conduct a case study in the context of the latest preCICE distribution, which is currently preCICE \texttt{v2211.0}.
The preCICE distribution consists out of the preCICE core library, as well as some tools, bindings, adapters, tutorials, the website and documentation, and the preCICE VM\footnote{\url{https://precice.org/installation-distribution.html}}.
Table \ref{table:label-distribution} shows an overview over all packages provided by the preCICE distribution and their respected versions.

\begin{figure*}[!t]
  \normalsize
  \caption{Overview of preCICE distribution}
  \label{table:label-distribution}
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \bfseries Package & \bfseries Type & \bfseries Build System & \bfseries Version \\
    \hline
    precice & library & cmake & 2.5.0 \\
    \hline
    fortran-module & bindings & make & 9e3f405 \\
    \hline
    julia & bindings & julia & v2.5.0 \\
    \hline
    matlab & bindings & matlab build script & v2.5.0.0 \\
    \hline
    pyprecice & bindings & setup.py & 2.5.0.1 \\
    \hline
    config-visualizer & tooling & setup.py & 60f2165 \\
    \hline
    precice-aste & adapter & cmake & 3.0.0 \\
    \hline
    dealii & solver & cmake & 9.4.1 \\
    \hline
    precice-dealii-adapter & adapter & cmake & dbb25bea \\
    \hline
    precice-calculix-adapter & adapter & makefile & 2.20 \\
    \hline
    fenics & solver & cmake + setup.py & 2019.1.0 \\
    \hline
    precice-fenics-adapter & adapter & setup.py & 1.4.0 \\
    \hline
    precice-dune & adapter & scripts + cmake & 2.8.0 \\
    \hline
    Dune-fem & library & setup.py & 2.8.0.0 \\
    \hline
    code-aster & solver & custom build system in python & 14.6.0 \\
    \hline
    openfoam & solver & wmake/Allwmake & 2206 \\
    \hline
    openfoam-adapter & adapter & wmake/Allwmake & 1.2.1 \\
    \hline
    Precice-su2 & solver + adapter & patch script + autoconf & 6.0.0 \\
    \hline
    Nutils & library & setup.py & 7.0.0 \\
    \hline
  \end{tabular}
\end{figure*}
